A_pilot_1

### 2018-08-31 experiments/A_pilot_1/writeup/A_pilot_1.Rmd
A update Rmd and project str

```{r load libraries, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source('summarySEwithin2.R')
source("A_pilot_1_functions/pretty_coef_table.R")
```

@@

```{r, "lmer 1 compare different rt metrics using the same model structure", warning=FALSE, cache=TRUE}
lmer1.ms  <- lmer(data=dat, rt_ms ~         vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.log <- lmer(data=dat, rt_log ~        vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.rcp <- lmer(data=dat, rt_reciprocal ~ vag + subit + quan + gap + side + (1|subject) + (1|item))

models <- 
rbind(
  cbind(tidy(lmer1.ms),model="ms"), 
  cbind(tidy(lmer1.log),model="log"), 
  cbind(tidy(lmer1.rcp),model="rcp")
)

@@

```{r lmer on logrt, warning=FALSE, cache=TRUE, fig.width=6, fig.height=2}
lmer2.log <- lmer(data=dat, rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))

dwplot(lmer2.log %>% tidy() %>% filter(group=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) +
  xlab("Coefficient") +
  ggtitle("rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)") + 
  theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8))

lmer2.rcp <- lmer(data=dat, rt_reciprocal~subit*vag + (vag|subject) + (vag|item))

# lmer3 is closer to the original anova than lmer2
lmer3 <- lmer(data=dat, rt_reciprocal~vag*subit+quan+gap + (vag+subit|subject) + (vag|item))

dwplot(lmer3 %>% tidy() %>% filter(group=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) +
  xlab("Coefficient") + 
  ggtitle("rt_reciprocal ~ vag * subit + quan + gap + (vag+subit|subject) + (vag|item)") + 
  theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8))
```

>>>>

```{r load libraries, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(grid)
library(gridExtra)
source("A_pilot_1_functions/pretty_coef_table.R")
source("A_pilot_1_functions/summarySEwithin2.R")
```

@@

```{r, "lmer 1 compare different rt metrics using the same model structure", warning=FALSE}
lmer1.ms  <- lmer(data=dat, rt_ms ~         vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.log <- lmer(data=dat, rt_log ~        vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.rcp <- lmer(data=dat, rt_reciprocal ~ vag + subit + quan + gap + side + (1|subject) + (1|item))
```

```{r}
models <- 
rbind(
  cbind(tidy(lmer1.ms),model="ms"), 
  cbind(tidy(lmer1.log),model="log"), 
  cbind(tidy(lmer1.rcp),model="rcp")
)

@@

```{r lmer on logrt, warning=FALSE}
lmer2.log <- lmer(data=dat, rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))
```

```{r, fig.width=6, fig.height=2}
dwplot(lmer2.log %>% tidy() %>% filter(effect=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) +
  xlab("Coefficient") +
  ggtitle("rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)") + 
  theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8))
```

```{r}
lmer2.rcp <- lmer(data=dat, rt_reciprocal~subit*vag + (vag|subject) + (vag|item))
```

```{r}
# lmer3 is closer to the original anova than lmer2
lmer3 <- lmer(data=dat, rt_reciprocal~vag*subit+quan+gap + (vag+subit|subject) + (vag|item))
```

```{r, fig.width=6, fig.height=2}
dwplot(lmer3 %>% tidy() %>% filter(effect=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) +
  xlab("Coefficient") + 
  ggtitle("rt_reciprocal ~ vag * subit + quan + gap + (vag+subit|subject) + (vag|item)") + 
  theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8))
```
